Autonomous Oceanographic Data Collection towards Estimating Excursion Sets of Vector-valued Random Fields

### 2020-06-12 main_new.tex
Updates from Overleaf

\section*{Appendix}

Proof of Proposition \ref{propo1}:

\begin{proof}
	That $\mes(\es)$ defines indeed a random variable follows from Fubini's theorem 
	relying on the joint measurability of 
	$(\x, \omega) \to \mathbbm{1}_{\es(\omega)}(\x)$, 
	%= \mathbf{1}_{\xi_{\x}(\omega) \in T}$ and Fubini's theorem.  
	itself inherited from the assumed measurability for  
	$(\x, \omega) \to \gp[\x](\omega)$ and $T$, respectively. From there, following the steps of Robbins' theorem \cite{Robins1944}, we find that 
	\begin{equation*}
	\begin{split}
	\mathbb{E}[\mes(\es)^{r}]
	&=\mathbb{E}\left[\left(\int_{D} \mathbbm{1}_{\gp[u] \in T} ~d\mes(u) \right)^{r} \right]
	=\mathbb{E}\left[ \prod_{i=1}^{r} \left(
	\int_{D} \mathbbm{1}_{\gp[\uu^{(i)}] \in T} ~d\mes(\uu^{(i)}) 
	\right) \right] \\
	&
	=
	%\mathbb{E}\left[
	%\int_{D^{r}}
	%\prod_{i=1}^{r}
	%\mathbf{1}_{\gp[\uu^{(i)}] \in T}
	%\productMeasure
	%\right]
	%=
	\mathbb{E}\left[
	\int_{D^{r}}
	\mathbbm{1}_{\gp[\uu^{(1)}] \in T,\dots, \gp[\uu^{(r)}]  \in T}
	\productMeasure
	\right]
	%\\
	%&=\int_{D^{r}} \mathbb{E}\left[\mathbf{1}_{\gp[\bm{u}] \in T^r} \right] \productMeasure \\
	%&
	=\int_{D^{r}}
	\jointExcuProb 
	\productMeasure.
	\end{split}
	\end{equation*}   
	The rest consists in expliciting the probability of $T\times \dots \times T$ under the multivariate Gaussian distribution of  
	$\left(\gp[u^{(1)}], \dots,  \gp[u^{(r)}] \right)$. 
\end{proof}

Proof of Proposition \ref{propo2}:

\begin{proof}
	By definition of $\Phi_{p}$, for $N\sim \mathcal{N}_{p}(0_{p},\covN)$, 
	$$
	\mathbb{P}(N\leq a + BV | V)
	=
	\varPhi_{p}\left( a + BV; \covN \right).
	$$
	Now for $\varPhi_{p}\left( a + BV; \covN \right)^h$, provided that the probability space is sufficiently large to accomodate $h$ independent Gaussian random vectors $N_i\sim \mathcal{N}_{p}(0,\covN)$ (which is silently assumed here), using the former equality delivers 
	$$
	\varPhi_{p}\left( a + BV; \covN \right)^h
	=
	\prod_{i=1}^h \mathbb{P}(N_i\leq a + BV | V).
	$$
	Now by independence of the $N_i$'s we obtain the joint conditional probability 
	$$
	\prod_{i=1}^h \mathbb{P}(N_i\leq a + BV | V)
	=
	\mathbb{P}(N_1\leq a + BV, \dots, N_h\leq a + BV| V),
	$$
	whereof, by virtue of the law of total expectation, 
	\begin{equation*}
	\begin{split}
	\mathbb{E}\left[ \varPhi_{p}\left( a + BV; \covN \right)^h \right]
	&=\mathbb{E}\left[\mathbb{P}(N_1\leq a + BV, \dots, N_h\leq a + BV| V)\right]\\
	&=\mathbb{P}(N_1\leq a + BV, \dots, N_h\leq a + BV)\\
	&=\mathbb{P}(W_1 \leq a, \dots, W_h\leq a)\\
	&=\varPhi_{ph}
	\left(
	1_{h} \otimes a
	;
	(1_{h}1_{h}')\otimes (B\Sigma_{V} B') + 
	I_{h}\otimes \covN
	\right),
	\end{split}
	\end{equation*}
	where $\mathbf{W}=(W_1,\dots,W_h)$ with $W_i=N_i- BV \ (1\leq i \leq h)$
	and the last line follows $\mathbf{W}$ forming a Gaussian vector (by global independence of the $N_i$'s and $V$) and from the definition of $\varPhi_{p h}$. The covariance matrix $\mathbf{\Sigma}$ of $\mathbf{W}$ is obtained by noting that $\operatorname{cov}(W_i,W_j)=B \covV B' + \delta_{ij} \covN \ 
	(i,j \in \{1,\dots,h\})$.
	%the latter concatenated Gaussian vector is obtained by straightfoward calculation. 
\end{proof}

Proof of Proposition \ref{propo3}.

\begin{remark}
	%    Note that the vector $\bm{a}$ is obtained by stacking $h_i$ times each $a_i$
	%\begin{equation*}
	%\bm{a} = \begin{pmatrix}
	%    \bm{a}_1\\ \vdots\\ \bm{a}_g\end{pmatrix},~
	%\bm{a}_i =
	%\begin{pmatrix}
	%    a_i\\ \vdots\\ a_i\end{pmatrix}
	%\in\mathbb{R}^{l\times h_i}\end{equation*}
	%and the covariance matrix is obtained by similar stacking
	Using blockwise representation for the blocks themselves delivers %$\bm{\Sigma}$ can be expressed as follows
	\begin{equation*}
	%    \bm{\Sigma} = \begin{pmatrix}
	%        \Sigma_{11} & & \Sigma_{1g}\\
	%        & \ddots &\\
	%        \Sigma_{g1}&   & \Sigma_{gg}
	%\end{pmatrix},~
	\Sigma_{ij} =
	\begin{pmatrix}
	B_i\Sigma_{V} B_j' & \dots & B_i\Sigma_{V} B_j'\\
	\vdots & & \vdots\\
	B_i\Sigma_{V} B_j' & \dots & B_i\Sigma_{V} B_j'\\
	\end{pmatrix}
	+
	\delta_{ij}
	\begin{pmatrix}
	\covN_i & &\\
	& \ddots &\\
	&   & \covN_i
	\end{pmatrix}%\in\mathbb{R}^{lh_i\times lh_j}
	\end{equation*}
	Here each $\Sigma_{ij}$ is made of $h_i$ times $h_j$
	(vertically/horizontally) $p \times p$ sub-blocks, hence possesses $ph_i$ lines and $ph_j$ columns.
\end{remark}

%Proof TODO along with notation polish.

\begin{proof}
	The proof relies (again) heavily on the fact that, by definition of $\Phi_{p}$, for any covariance matrix $\covN \in \R^{p \times p}$, $a\in \R^p$, $B\in \R^{p \times q}$, and $N\sim \mathcal{N}_{p}(0_{p},\covN)$, 
	$$
	\mathbb{P}(N\leq a + BV | V)
	=
	\varPhi_{p}\left( a + BV; \covN \right).
	$$
	In particular, for globally independent $N_{i,j} \sim \mathcal{N}_{p}(0_{p},\covN_i)$ $(1\leq j \leq h_i, 1\leq i \leq g)$, 
	\begin{equation*}
	\begin{split}
	\prod_{i=1}^{g} \varPhi_{p}\left(a_i + B_{i}V; \covN_{i} \right)^{h_i}
	&=
	\prod_{i=1}^{g}
	\prod_{j=1}^{h_{i}}
	\mathbb{P}(N_{i,j}\leq a_i + B_i V | V)\\
	&=\mathbb{P}(N_{1,1}\leq a_1 + B_1 V, \dots, N_{g,h_{g}}\leq a_g + B_g V | V),
	\end{split} 
	\end{equation*}
	so that, by the law of total expectation, 
	\begin{equation*}
	\begin{split}
	\mathbb{E}\left[ \prod_{i=1}^{g} \varPhi_{p}\left(a_i + B_{i}V; \covN_{i} \right)^{h_i} \right]
	=
	\mathbb{P}(W_{1} \leq 1_{h_{1}} \otimes a_1, \dots, W_{g} \leq 1_{h_{g}} \otimes a_g)
	\end{split}
	\end{equation*}
	where 
	$W_{1}=(N_{1,1}- B_1 V, \dots, N_{1,h_{1}}- B_1 V), 
	W_{2}=(N_{2,1}- B_2 V, \dots, N_{2,h_{2}}- B_2 V), 
	\dots, W_{g}=(N_{g,1}- B_g V, \dots, N_{g,h_{g}}- B_g V)$. Noting that $\mathbf{W}=(W_1,\dots, W_g)$ is a centred $p H$-dimensional Gaussian random vector, we finally obtain that 
	\begin{equation*}
	\begin{split}
	\mathbb{E}\left[ \prod_{i=1}^{g} \varPhi_{p}\left(a_i + B_{i}V; \covN_{i} \right)^{h_i} \right]
	=
	\varPhi_{p H}\left(\bm{a};\mathbf{\Sigma}\right),
	\end{split}
	\end{equation*}
	with $\bm{a}=(1_{h_{1}} \otimes a_1, \dots, 1_{h_{g}} \otimes a_g)$ and $\bm{\Sigma}=(\operatorname{cov}(W_i,W_j))_{i,j \in \{1,\dots, g\}}$.
\end{proof}

>>>>

\section*{Appendix}
\input{appendix}
